Before starting to develop and implement Miraihilate, I first designed wireframe mockups to decide what the interface would look like before implementation. The wireframes were designed in \href{https://balsamiq.com}{Balsamiq}, and will be used to gain initial feedback on the layout of the design rather than usability, before designing a working prototype for usability feedback.

\subsection{Mockup Design}

The mockups that I designed for this initial feedback are of primary components of the system which users have the most interaction with. This includes:
\begin{itemize}
	\item{Client Interface}
	\item{Advanced Scanning}
	\item{Scan Logs}
\end{itemize}

\subsection{Feedback Survey}

\subsubsection{Recruitment}

To conduct the feedback survey, I recruited participants who are studying Computer Science or a similar discipline. I did this by confronting potential participants from within the MACS department at Heriot-Watt university.

\vspace{0.5cm}

After finding a candidate willing to participate in the feedback survey they had to first sign a consent form, shown in Appendix A.1, informing them about the aims of the survey as well as to notify that they can withdraw their results at any time. They were then given three question sheets shown in Appendices A.2-4 to answer, each of which had images of the respective mockup being surveyed.

\subsubsection{Initial Feedback Analysis}

Explain feedback I gained...

\subsection{Pre-Implementation}

To reflect on the feedback survey results, I can conclude that there were minimal comments made to the structure of the design. Because the designs were only mockups, the feedback is only intended for helping with designing the interfaces for the client program before conducting a final usability study on a working prototype. Overall, based on the analysis of the feedback I gained, there will be no major changes to the interfaces, aside from reducing the amount of whitespace. One comment however was that it would have been better to show how the scan result text would be shown. This is not a major factor for feedback on the structure of the interface, but this factor will be more evident in the usability study on the working prototype.
