\begin{center}
	\textbf{Usability Survey Consent Form}\par
	\textbf{Participant No.}\par
	\textbf{Project:} Building and testing a white-hat botnet checker for evaluating the effectiveness of Mirai against other botnet malware
\end{center}

The objective of the experiment is to provide useful usability information of Miraihilate, a botnet checker program. The program is primarily used to scan a range of IP addresses to find devices that are vulnerable to Mirai malware. Prior to the study, you will be given a question sheet asking brief questions about your technical competence. In the study, you will be given the Miraihilate prototype program to conduct four scenarios given to you and answer questions about them.

\vspace{0.5cm}

All results will be held in strict confidence, ensuring the privacy of all participants. There will be no record kept that would allow your results to be tracked back to you. All data will also be held securely in a locked office. A feedback sheet (containing summaries of the data mentioned above) will be sent to all participants who request it, after the data has been analysed. Your participation in this experiment will have no effect on your marks for any subject at this, or any other university.

\vspace{0.5cm}

You may withdraw from the experiment at any time without prejudice, and any data already recorded will be deleted.

\vspace{0.5cm}

\begin{table}[h]
\centering
\begin{tabular}{ll}
\hline
Project Student:     & Project Supervisor:    \\
Ryan Shah            & Mike Just              \\
Email: rs10@hw.ac.uk & Email: m.just@hw.ac.uk \\ \hline
\end{tabular}
\end{table}

Name:\par
Signed:\par
Date:\par
Email Address:\par

\vspace{0.5cm}

I would like to receive information on the results of this study (circle \textbf{one}): \textbf{Yes / No}
