\begin{center}
	\textbf{Usability Survey Pre-Study Questionnaire}\par
	\textbf{Participant No.}\par
\end{center}

Below is a series of questions aimed to gather information about your technical competence, please answer all questions.

\vspace{0.5cm}

\textbf{1.} On a typical day, how much time do you spend on a computer? (Circle one)
\begin{center}
	\begin{table}[h]
	\begin{tabularx}{\textwidth}{XXXXXX}
	\multicolumn{6}{l}{} \\
	\centering
	None & > 30 mins & 30-60 mins & 1-2 hours & 2-4 hours & > 4 hours \\
	\end{tabularx}
	\end{table}
\end{center}

\textbf{2.} Have you ever used a unix-based operating system, such as Linux or macOS? \tab Yes / No

\vspace{0.5cm}

\textbf{3.} If yes, on a scale of 1-10 how confident are you with using a unix-based operating system? (If no, proceed to question \textbf{4.})

\begin{center}
	\begin{table}[h]
	\begin{tabularx}{\textwidth}{XXXXXXXXXX}
	\multicolumn{5}{l}{Not Confident} & \multicolumn{5}{r}{Very Confident} \\
	\centering
	1    & 2    & 3    & 4    & 5    & 6    & 7    & 8    & 9    & 10
	\end{tabularx}
	\end{table}
\end{center}

\textbf{4.} On a scale of 1-10 how confident are you with troubleshooting (fixing a problem) a computer program?

\begin{center}
	\begin{table}[h]
	\begin{tabularx}{\textwidth}{XXXXXXXXXX}
	\multicolumn{5}{l}{Not Confident} & \multicolumn{5}{r}{Very Confident} \\
	\centering
	1    & 2    & 3    & 4    & 5    & 6    & 7    & 8    & 9    & 10
	\end{tabularx}
	\end{table}
\end{center}

\textbf{5.} Have you had any experience with using a command-line interface, such as Command Prompt or Terminal? \tab Yes / No

\vspace{2cm}

\textbf{6.} If yes, how would you rate your experience with a command line interface? (If no, proceed to question \textbf{7.})

\begin{center}
	\begin{table}[h]
	\begin{tabularx}{\textwidth}{XXXXXXXXXX}
	\multicolumn{5}{l}{Inexperienced} & \multicolumn{5}{r}{Experienced} \\
	\centering
	1    & 2    & 3    & 4    & 5    & 6    & 7    & 8    & 9    & 10
	\end{tabularx}
	\end{table}
\end{center}

\textbf{7.} Have you had any experience with scanning programs, such as an antivirus? \tab Yes / No

\vspace{0.5cm}

\textbf{8.} Have you had any experience with network tools (i.e. network scanners, command-line network utilities) \tab Yes / No
