\begin{center}
	\textbf{Scenario Two}\par
	\textbf{Participant No.}\par
\end{center}

In this scenario, you will be performing a quick scan and viewing your recent scan history. Please follow all the steps below.

\vspace{0.5cm}

\begin{enumerate}
	\item{Run Miraihilate by double clicking the executable file named \textit{miraihilate.jar}}
	\item{You will be asked to first login, so use the email address you entered and password generated for you from the first scenario.}
	\item{Spend a brief amount of time looking at the features of the main interface you see.}
	\item{
		Locate the quick scan panel and fill in the field with the following details:\par
		\begin{lstlisting}
			IP Address: 127.0.0.1
			CIDR: 30
			Change Password: Unticked
			Notify Device: Ticked
		\end{lstlisting}
		\par Press the help button if you want more information on what these things mean.
	}
	\item{Press the quick scan button.}
	\item{Open the "Scan History" window.}
	\item{Check that you can see your scan.}
\end{enumerate}

\begin{center}
	\line(1,0){450}
\end{center}

After completing the above scenario, please answer all questions below.

\vspace{0.5cm}

\textbf{1.} On a scale of 1-10 how easy was it to login to Miraihilate?

\begin{table}[h]
	\centering
	\begin{tabularx}{\textwidth}{XXXXXXXXXX}
		\multicolumn{5}{l}{Very Difficult} & \multicolumn{5}{r}{Very Easy} \\
		\centering
		1    & 2    & 3    & 4    & 5    & 6    & 7    & 8    & 9    & 10
	\end{tabularx}
\end{table}

\clearpage

\textbf{2.} Are there any improvements or changes you would make to the login?

\vspace{3cm}

\textbf{3.} Looking at the main interface after logging in to Miraihilate, are there any improvements or changes you would make to improve the layout and usability of the main interface?

\vspace{3cm}

\textbf{4.} On a scale of 1-10 how easy was it to perform a quick scan?

\begin{table}[h]
	\centering
	\begin{tabularx}{\textwidth}{XXXXXXXXXX}
		\multicolumn{5}{l}{Very Difficult} & \multicolumn{5}{r}{Very Easy} \\
		\centering
		1    & 2    & 3    & 4    & 5    & 6    & 7    & 8    & 9    & 10
	\end{tabularx}
\end{table}

\textbf{5.} Are there any improvements or changes you would make to the quick scan panel to improve its usability?

\vspace{3cm}

\textbf{6.} How easy was it to view your scan history?

\begin{table}[h]
	\centering
	\begin{tabularx}{\textwidth}{XXXXXXXXXX}
		\multicolumn{5}{l}{Very Difficult} & \multicolumn{5}{r}{Very Easy} \\
		\centering
		1    & 2    & 3    & 4    & 5    & 6    & 7    & 8    & 9    & 10
	\end{tabularx}
\end{table}

\textbf{7.} Are there any improvements or changes you would make to the scan history interface?

\clearpage

\textbf{8.} Ultimately, how confident were you performing a quick scan on a network using Miraihilate?

\begin{table}[h]
	\centering
	\begin{tabularx}{\textwidth}{XXXXXXXXXX}
		\multicolumn{5}{l}{Not Confident} & \multicolumn{5}{r}{Very Confident} \\
		\centering
		1    & 2    & 3    & 4    & 5    & 6    & 7    & 8    & 9    & 10
	\end{tabularx}
\end{table}

\textbf{9.} Do you have any final comments about the tasks or the interfaces used in this scenario?
