\begin{center}
	\textbf{Scenario One}\par
	\textbf{Participant No.}\par
\end{center}

In this scenario, you will be setting up Miraihilate. This program will ask you to enter details about yourself to setup your own user for the system, which will be used for the rest of the study. Please follow all the steps below.

\vspace{0.5cm}

\begin{enumerate}
	\item{
		The terminal window will already be open for you in the correct directory, so run the following command:\par
		\begin{lstlisting}[language=bash]
			python3 setup.py
		\end{lstlisting}
	}
	\item{Follow the remaining steps on the command-line interface.}
	\item{After finishing entering your details, you will be given a securely generated password. Make a note of this, as this will be used for the rest of the scenarios.}
\end{enumerate}

\begin{center}
	Note: You will see that the Miraihilate client program will be downloaded in the same directory.
\end{center}

\begin{center}
	\line(1,0){450}
\end{center}

After completing the above scenario, please answer all questions below.

\vspace{0.5cm}

\textbf{1.} Was it easy to setup Miraihilate using the command-line interface?

\begin{table}[h]
	\centering
	\begin{tabularx}{\textwidth}{XXXXXXXXXX}
		\multicolumn{5}{l}{Very Difficult} & \multicolumn{5}{r}{Very Easy} \\
		\centering
		1    & 2    & 3    & 4    & 5    & 6    & 7    & 8    & 9    & 10
	\end{tabularx}
\end{table}

\textbf{2.} Would it be more preferable to have a graphical interface rather than using the command-line to setup the program? \tab Yes / No

\vspace{0.5cm}

\textbf{3.} Are there any other improvements or changes you would make to the current setup utility?
