\begin{center}
	\textbf{Scenario Four}\par
	\textbf{Participant No.}\par
\end{center}

In this scenario, you will be performing an advanced scan. The procedure is similar to performing a quick scan, with the added functionality of providing a timeout and extra commands to the device. Please follow all the steps below.

\vspace{0.5cm}

\begin{enumerate}
	\item{Open the "Advanced Scan" window.}
	\item{
		Locate the quick scan panel and fill in the field with the following details:\par
		\begin{lstlisting}
			IP Address: 127.0.0.1
			CIDR: 30
			Change Password: Unticked
			Notify Device: Ticked
		\end{lstlisting}
		\par Press the help button if you want more information on what these things mean.
	}
	\item{
		Choose a timeout value under 8 seconds and enter one or more commands from the following list:
		\begin{lstlisting}
			# Create an alert with Hello World
			- notify-send 'Hello World'

			# Create a directory in the root user home directory called hello
			- mkdir hello

			# Show who is logged on and what they are doing
			- w

			# Create a directory called study and create a file called test.txt inside it, containing "Hello World"
			- mkdir study; cd study; echo "Hello World" > test.txt

			# List items in the root user home directory
			- ls
		\end{lstlisting}
	}
	\item{Pressed the Perform Advanced Scan button.}
	\item{Go back to the main interface and see your scan in the "Recent Scan" panel.}
\end{enumerate}

\begin{center}
	\line(1,0){450}
\end{center}

After completing the above scenario, please answer all questions below.

\vspace{0.5cm}

\textbf{1.} On a scale of 1-10 how easy was it to perform the advanced scan?

\begin{table}[h]
	\centering
	\begin{tabularx}{\textwidth}{XXXXXXXXXX}
		\multicolumn{5}{l}{Very Difficult} & \multicolumn{5}{r}{Very Easy} \\
		\centering
		1    & 2    & 3    & 4    & 5    & 6    & 7    & 8    & 9    & 10
	\end{tabularx}
\end{table}

\textbf{2.} What timeout and commands did you enter in the advanced scan?

\vspace{3cm}

\textbf{3.} Are there any improvements or changes you would make to the quick scan panel to improve its usability?
