\raggedright

Since the progression of network attacks, botnets have become
increasingly powerful. There have been many large-scale botnets,
but there were some which had incredible impacts on regular
internet users\textsuperscript{\cite{goodman2017survey}}.

\vspace{0.5cm}

One such botnet, first discovered in 2008, was called Grum. This
bot was one of the largest in terms of distributing spam email
traffic. It was responsible for up to 26\% of the worlds spam
email traffic, capable of emitting up to 40 billion messages
a day. Another botnet, which was similar in the way that it operated,
was called Windigo. This only emitted around 35 million emails a
day but is infamous because it infected a large number of Linux
servers. This raised a lot of security questions due to the fact
that at the time more than 60\% of web servers use a Linux
operating system.

\vspace{0.5cm}

ZeroAccess was also another powerful botnet in history. Unlike others,
this botnet was used for click fraud and bitcoin mining. It used its
mass of distributed devices for CPU and GPU bitcoin mining and for
performing fraudulent clicks on pay-per-click ad revenue websites
to make money illegally. It was a very resilient and powerful P2P
botnet.

\vspace{0.5cm}

Two botnets named Metulji and Mariposa\textsuperscript{\cite{sinha2010insights}} also make it on the list of
infamous botnets in history. These two botnets operate differently
to some of the others. This is because they were developed from a
\textit{Butterfly Framework}, a kit used for creating botnets. Both
botnets managed to enslave greater than 10 million devices each.
Metulji was thought to have stolen millions of dollars with of private
passwords, credit card details and social security numbers. This made
it a very scary botnet to individuals whose personal information had
been compromised.
Both botnets, however, were shut down. One flaw in the Butterfly Framework,
was that recrods were kept for who paid for the service, unveiling
the creators of both botnets.