\raggedright

The "Internet of Things" (IoT) is a concept that has the potential
to impact how we live from day to day, but what impact does it have on people, if any?
The concept surrounds the connection of any device, so long as it can be turned on and off, to the Internet and other connected devices.
The term IoT \textit{generally} refers to the "networked interconnection of everyday objects, which are often equipped with ubiquitous intelligence"\textsuperscript{\cite{vermesan2011internet}}.

\vspace{0.5cm}

In this collection there are a vast amount of objects, which include
smart home systems, self-driving cars, and even wearable devices.
Objects and/or devices that have in-built sensors are connected to an IoT platform, which collects the data from them and shares the most important information with other applications developed to address specific user needs.

However, with the sheer number of these devices constantly increasing,
newer problems are introduced relating to them. More specifically, the security of these devices becomes a greater issue, as new vulnerabilities\textsuperscript{\cite{hole2017analysis}} are created and identified.

\vspace{0.5cm}

With these vulnerabilities left open to the Internet, and some not being identified, threats to the security of these devices is an important issue that needs to be addressed.
Most of these devices dont directly interface with the user(s) associated with the device,
and therefore it becomes difficult to identify any abnormal behaviour.

Recent events show a trend where IoT devices are becoming increasingly involved in cyber-attacks, with reports indicating IoT attacks have grown 280\% in the first half of 2017\textsuperscript{\cite{f5article}}. Therefore, more secure communication with the Internet and eachother to ensure safety of keeping and using these devices in people's day-to-day routines.